Sea: A lightweight data-placement library for Big Data scientific computing

### 2022-05-18 paper/sea-comp/paper.tex
updated acknowdlegements and bibliographies

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Hayot-Sasson\MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for
Computer Society Journals} \IEEEtitleabstractindextext{%
\begin{abstract}
    The recent influx of open scientific data has contributed to the
    transitioning of scientific computing from compute intensive to data intensive.
    Whereas many Big Data
frameworks exist that minimize the cost of data transfers, few scientific
applications integrate these frameworks or adopt data-placement strategies to mitigate the costs.
Scientific applications commonly rely on well-established command-line tools that would require complete reinstrumentation
in order to incorporate existing frameworks.
We developed Sea as a means to enable data-placement strategies for scientific
applications executing on HPC clusters without the need to reinstrument
workflows. Sea leverages GNU C library interception to intercept POSIX-compliant
file system calls made by the applications. We designed a performance model and
evaluated the performance of Sea on a synthetic data-intensive application
processing a representative neuroimaging dataset (the Big Brain). Our results
demonstrate that Sea significantly improves performance, up to a factor of
3$\times$.

@@

@@

\begin{IEEEbiography}{Val\'erie Hayot-Sasson}
\end{IEEEbiography}
\begin{IEEEbiography}{Tristan Glatard}
\end{IEEEbiography}
\end{document}

>>>>

% The paper headers
% \markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
% {Hayot-Sasson\MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for
% Computer Society Journals} 
\IEEEtitleabstractindextext{%
\begin{abstract}
    The recent influx of open scientific data has contributed to the
    transitioning of scientific computing from compute intensive to data intensive.
    Whereas many Big Data
frameworks exist that minimize the cost of data transfers, few scientific
applications integrate these frameworks or adopt data-placement strategies to mitigate the costs.
Scientific applications commonly rely on well-established command-line tools that would require complete reinstrumentation
in order to incorporate existing frameworks.
We developed Sea as a means to enable data-placement strategies for scientific
applications executing on HPC clusters without the need to reinstrument
workflows. Sea leverages GNU C library interception to intercept POSIX-compliant
file system calls made by the applications. We designed a performance model and
evaluated the performance of Sea on a synthetic data-intensive application
processing a representative neuroimaging dataset (the Big Brain). Our results
demonstrate that Sea significantly improves performance, up to a factor of
3$\times$.

@@

\section*{Acknowlegments}
Val\'erie Hayot-Sasson was funded by the Canadian Open Neuroscience Platform (CONP) Scholar Award.
This work was also supported by the Canada Foundation for Innovation as well as the Canada Research Chairs program.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biopics/vhs.pdf}}]{Val\'erie Hayot-Sasson} is a PhD student at Concordia University in the Big Data for Neuroinformatics lab. Her research interests focus on studying the effects of data transfers on Big Data scientific application.
\end{IEEEbiography}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biopics/md}}]{Mathieu Dugr\'e} is a Ph.D. student at the Big Data Infrastructure for Neuroinformatics lab at Concordia University, Montreal, Canada. His research interests are in Big Data performance techniques for neuroimaging applications.

\end{IEEEbiography}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{biopics/tg}}]{Tristan Glatard} is Associate Professor in the
Department of Computer Science and Software
Engineering at Concordia University in Montreal,
and Canada Research Chair (Tier II) on Big
Data Infrastructures for Neuroinformatics. Before
that, he was research scientist at the French Na-
tional Centre for Scientific Research and Visiting
Scholar at McGill University.
\end{IEEEbiography}
\end{document}
